%%%%%%%%%%%%%%%%%%%%%%%%%% Proposal of the first year %%%%%%%%%%%%%
\documentclass[a4paper,11pt, english]{article}

%%%%%%%%%%%% Packages
\usepackage[table]{xcolor}         			% colored text
\usepackage{smartdiagram}
\usepackage{adjustbox}
\usepackage{changepage}
\usepackage{standalone}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{lipsum,calc}
\usepackage{array,longtable}
\usepackage{tabularx} 
\usepackage{collcell}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[all]{xy}         			% diagrams
\usepackage{amssymb}				% \mathbb and others
\usepackage{amsthm}				% theorem styles
\usepackage{amsmath}				% Declare math operator
\usepackage{enumerate}       			% many possible numerations
\usepackage{manfnt,xspace}			%% added package
\usepackage[a4paper,top=3cm, bottom=3cm, left=3cm, right=3cm]{geometry}
\usepackage{pifont}% http://ctan.org/pkg/pifont
%\usepackage{natbib}


%\usepackage[backend=bibtex,style=numeric,citestyle=numeric]{biblatex}
\usepackage[backend=bibtex,maxbibnames=99]{biblatex}

\addbibresource{proposal_correct}
                        

\newcommand{\cmark}{\ding{51}}                    
                        
\definecolor{lightgreen}{HTML}{CCFF66}
\definecolor{green}{HTML}{66FF66}
\definecolor{lightyellow}{HTML}{FFFF66}
\definecolor{orange}{HTML}{FF9900}
\definecolor{red}{HTML}{FF3333}
\definecolor{cyan}{HTML}{00CCFF}
\definecolor{blue}{HTML}{0000FF}
\definecolor{blue-violet}{rgb}{0.54, 0.17, 0.89}
                        

%%%%% Font Macros
\usepackage{dsfont}
\usepackage[T1]{fontenc}
\def\lqq{{\fontencoding{T1}\selectfont\guillemotleft}}
\def\rqq{{\fontencoding{T1}\selectfont\guillemotright}}
\DeclareFontFamily{OT1}{pzc}{}
\DeclareFontShape{OT1}{pzc}{m}{it}{<->s*[1.10]pzcmi7t}{}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}


\pgfplotsset{compat=1.9}

%%%%%%%%%%%%%%%%%%%%%%% title

\title{\vspace{0cm}
\hrule
\vspace{1cm}
\centerline{\LARGE{Thesis Proposal:}}
\vspace{0.5cm}
\centerline{\LARGE {\bf The Role of Embeddings in Data-Driven Augmentation}}
%\centerline{\LARGE{\bf }}
}

%\title{\begin{Large}Research Proposal\end{Large}}
\author{Federico Dassereto}
\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DOCUMENT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle
\hrule 
\vspace{1cm}

\begin{abstract}
    %A-o meu neuo gh'é neue nae neue: a ciù neua de neue nae neue a n'eu anâ.    
    Querying data lakes containing a large amount of unstructured data is a difficult task, accentuated by the facility of producing data due to the rise of the World Wide Web. A traditional operation on data lakes is to search for joinable and unionable tables, to find tables related to specific user requests. Existing approaches search for columns with the best overlap possible, returning columns from tables in data lakes with high joining or unionability rating. These approaches fail to capture the situation in which a data scientist wants to find related tables related to a particular query table when she is trying to build a machine learning model to predict a column of her query table. The reason for which existing approaches fail is that they do not consider the impact that a joining table has on the predicting tasks, due to the lack of semantic surrounding the data lake. 

    The goal of the thesis is to define an automatic table augmentation framework, to improve the performance of machine learning models in predicting target columns of a query table. The idea is to start by studying the augmentation problem as a problem on data lakes only, with measures and concepts derived from information theory and functional dependencies, and then integration embeddings in the process. Embeddings will be integrated by mapping tables to knowledge bases and exploiting their semantics to automatically produce the augmentation. More precisely, the thesis will first propose a framework for automatic horizontal table augmentation in data lakes, allowing a data scientist to add relevant features to her query table from a ranking of joining tables. Furthermore, an extension comprehending a mapping of tables to knowledge bases and exploiting knowledge bases embeddings will be developed, to study the role of embeddings in automatic tables augmentation. Finally, to sum up, the previous results, an ad-hoc embedding algorithm for knowledge bases will be developed to emphasize the relevant properties a knowledge base should have to produce a relevant augmentation.
\end{abstract}

\input{sections/motivations.tex}

\input{sections/reference.tex}

\input{sections/related.tex}

\input{sections/goals.tex}

\input{sections/researchplan.tex}

%\section*{Acknowledgements}{So long, and thanks for all the fish.}



%\nocite{*}
\printbibliography

\end{document}